Trauma treatment delay

### 2023-11-14 manuscriptlongversion.Rmd
text

The 6,489 patients included in the study. 68% of the individuals
included were men, with the remaining 32% being women. The mean value
for the ISS score was 10.49, with the standard deviation being 11.4. The
patients had a mean GCS of ... with a standard deviation of ... The
majority of the patients had General care department as their highest
care level, followed by ICU, ER, OR and lastly specialized care
department. The mean respiratory rate in the overall group was ..., with
a standard deviation of ... The mean SBP was ..., having a standard
deviation of ... The majority of patients, 85%, were not intubated
during their stay in the hospital, followed by 9.1% intubated at the
hospital and 6% intubated prehospitaly. The mean age of the patients was
... years old, with a standard deviation of ... Most of the patients
arrived during on-call hours,..., with the rest arriving during working
hours. 67% of the patients arrived on a weekday, with the rest arriving
on the weekend.

@@

![](results.png)

>>>>

The 7,051 patients included in the study. 69% of the individuals
included were men, with the remaining 31% being women. The mean value
for the ISS score was 11.30, with the standard deviation being 13.22.
The majority of the patients had General care department as their
highest care level, followed by ER, ICU, OR and lastly specialized care
department. The majority of patients, 82%, were not intubated during
their stay in the hospital, followed by 9.2% intubated at the hospital
and 8.4% intubated prehospitaly. The mean age of the patients was 44.95
years old, with a standard deviation of 21.37. Most of the patients
arrived during on-call hour, 60%, with the rest arriving during working
hours. 67% of the patients arrived on a weekday, with the rest arriving
on the weekend.

@@

![](results1.png)

## Discussion

The results show that generally, patients do not systemically receive
delayed treatment because of a patient level factor.

As we see in the results, there was only one variable that, when
adjusted, had a correlation with the risk for a patient of receiving
delayed treatment, being the highest hospital care level. Compared with
having the ER as the highest care level, patients who were in the ICU or
the OR had a substantially lowered chance of receiving delayed
treatment.
